Staged Abstract Interpreter

### 2018-01-12 paper/paper.tex
misc

Store/set operations (join, update) is also expensive, generating efficient store implementation\cite{liang2014fast}.

@@

Another perspective: programs are data for an abstract interpreter, so if we have $n$ programs, 
then maybe there can be $n$ stages. 
Probably we can analyze first $m$ programs, and generate a residual abstract interpreter
waiting for the rest $(n-m)$ programs.

>>>>

Store/set operations (join, update) are also expensive, generating efficient store implementation\cite{liang2014fast}.

@@

Another perspective: programs are data for an abstract interpreter, so if we have $n$ programs, 
then maybe there can be $n$ stages. 
Probably we can analyze first $m$ programs, and generate a residual abstract interpreter
waiting for the rest $(n-m)$ programs.
The abstract interpreter itself might be a partial abstract interpreter.
